Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-06-06 paper/intro.tex
Revision about the citations

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems. The aim is to find the optimal design parameters that provide the
best circuit performance, which can be represented by a figure of merit (FOM)
real-valued function. Prior works about analog circuit optimization
include offline model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
global models of the FOM via manual calculation or regression with simulated
data and then optimize the cheap-to-evaluate models. The problem with this
approach is that the accurate models are usually hard to get. For example,
in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
a sparse polynomial model for an amplifier circuit with ten design parameters.

@@

In recent years, the Gaussian process (GP)~\cite{GPML} model has been
introduced for the automated design of analog circuits to reduce the
required number of circuit simulations. In~\cite{liu2014gaspad}, GP is combined
with differential evolution algorithm. Recently, the Bayesian optimization
(BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization
algorithm is firstly introduced for the single- and multi-objective
optimization of general analog circuits and has shown to be much more efficient
compared with other simulation-based approaches. In~\cite{wang2017efficient},
the Bayesian optimization algorithm is combined with adaptive Monte-Carlo
sampling to optimize the yield of analog circuits and static random-access
memory (SRAM).

@@

% TODO: Beiefly introduce my algorithm
All the batch Bayesian optimization algorithms mentioned above choose to use single acquisition function.
And except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition
function, other parallelization methods rely on a specific acquisition
function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
the knowledge gradient (KG) acquisition function must be used for the qKG algorithm. As is stated
in~\cite{hoffman2011portfolio}, no single acquisition function can always
outperform other acquisition functions. Relying on one acquisition function may
result in poor performance.

>>>>

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems. The aim is to find the optimal design parameters that provide the
best circuit performance, which can be represented by a figure of merit (FOM)
real-valued function. Prior works about analog circuit optimization
include offline model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
global models of the FOM via manual calculation or regression with simulated
data and then optimize the cheap-to-evaluate models. The problem with this
approach is that the accurate models are usually hard to get. For example,
in~\citet{wang2014enabling}, 100,000 randomly simulated points are used to train
a sparse polynomial model for an amplifier circuit with ten design parameters.

@@

In recent years, the Gaussian process (GP)~\cite{GPML} model has been
introduced for the automated design of analog circuits to reduce the
required number of circuit simulations. In~\citet{liu2014gaspad}, GP is combined
with differential evolution algorithm. Recently, the Bayesian optimization
(BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
circuit optimization. In~\citet{lyu2017efficient}, the Bayesian optimization
algorithm is firstly introduced for the single- and multi-objective
optimization of general analog circuits and has shown to be much more efficient
compared with other simulation-based approaches. In~\citet{wang2017efficient},
the Bayesian optimization algorithm is combined with adaptive Monte-Carlo
sampling to optimize the yield of analog circuits and static random-access
memory (SRAM).

@@

% TODO: Beiefly introduce my algorithm
All the batch Bayesian optimization algorithms mentioned above choose to use single acquisition function.
And except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition
function, other parallelization methods rely on a specific acquisition
function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
the knowledge gradient (KG) acquisition function must be used for the qKG algorithm. As is stated
in~\citet{hoffman2011portfolio}, no single acquisition function can always
outperform other acquisition functions. Relying on one acquisition function may
result in poor performance.
